---
title: "Study 2"
author: "Evan Valdes"
date: "9/24/2020"
output: html_document
---

```{r}
## Set working directory----
setwd("/Users/Evanvaldes1/Desktop/MASSEY/STUDY 2/CODE AND DATA")
```

```{r}
library(dplyr)
library(plyr)
library(stringr)
library(rms)
library(knitr)
library(readr)
library(surveydata)
library(Hmisc)
library(ggplot2)
library(psych)
library(haven)
library(stats)
library(lavaan)
library(tableone)
library(semPlot)
library(semTools)
library(tidyverse)
library(PerformanceAnalytics)
library(ggiraphExtra)
library(equaltestMI)
library(stargazer)
library(sjPlot)
library(apaTables)
library(interactions)
library(jtools)
library(mice)
library(BaylorEdPsych)
library(lme4)
library(styler)
library(readxl)
library(plm)
library(ggdag)
library(dagitty)
library(reghelper) # Simple slopes for interactions
library(mlma) # Multilevel mediation analysis
```

## Opening indvidual and country level data
```{r}
full_evan_dataset <- read_sav("Full Evan Dataset.zip")

countrylevelanalysis <- read_sav("Country level analysis for DI2.sav")

fullcountrylevel <- read_excel("Country-level index.xlsx")

```

## Country level exploratory analysis
```{r}
smallcla <- subset(fullcountrylevel, select = c(
  "Civil_Liberties", "Democracy", "Freedom", "Meritocracy", "GINI",
  "Individualism"
))

## civil liberties / democracy / freedom - make an index with these three
## Leave transparency as a single index

chart.Correlation(smallcla)
```

## factor analysis of CL/Democ/Freedom 
## Caculating a combined factor made up of CL/Democ/Freedom
```{r}
fullcountrylevel$`Country/Territory` <- as.factor(fullcountrylevel$`Country/Territory`)

## Recode CL / Democ so higher scores 
## indicate more CL and DEMOC
fullcountrylevel$Civil_Libertiesreversed <- recode(fullcountrylevel$Civil_Liberties, "1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1")

library(GPArotation)
ml <- fa(r = smallcla,
         nfactors = 3,
         rotate = "oblimin",
         fm= "ml",
         residuals = T) # Max likelihood

ml

fullcountrylevel$Economic_Social_Structure = NA

fullcountrylevel <- fullcountrylevel %>%
  mutate(Economic_Social_Structure = 
                 ifelse(`Country/Territory` == "Abkhazia", Civil_Liberties + Democracy + Freedom / 210,
    ifelse(`Country/Territory` == "Afghanistan", Civil_Liberties + Democracy + Freedom / 210,
           ifelse(`Country/Territory` == "Albania", Civil_Liberties + Democracy + Freedom / 210,
                  ifelse(`Country/Territory` == "Algeria", Civil_Liberties + Democracy + Freedom / 210,
                         ""
                         
                  )))))



mean(fullcountrylevel$Civil_Liberties + fullcountrylevel$Democracy + fullcountrylevel$Freedom / 210)
```

## Attaching country names to country level analysis DS
```{r}
countrylevelanalysis$Country <- as.character(countrylevelanalysis$Country)
countrylevelanalysis$Country[countrylevelanalysis$Country == 1] <- "Argentina"
countrylevelanalysis$Country[countrylevelanalysis$Country == 2] <- "Australia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 3] <- "Bolivia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 4] <- "Brazil"
countrylevelanalysis$Country[countrylevelanalysis$Country == 5] <- "Canada"
countrylevelanalysis$Country[countrylevelanalysis$Country == 6] <- "China"
countrylevelanalysis$Country[countrylevelanalysis$Country == 7] <- "Colombia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 8] <- "Egypt"
countrylevelanalysis$Country[countrylevelanalysis$Country == 9] <- "Finland"
countrylevelanalysis$Country[countrylevelanalysis$Country == 10] <- "Germany"
countrylevelanalysis$Country[countrylevelanalysis$Country == 11] <- "Greece"
countrylevelanalysis$Country[countrylevelanalysis$Country == 12] <- "Hong Kong"
countrylevelanalysis$Country[countrylevelanalysis$Country == 13] <- "Hungary"
countrylevelanalysis$Country[countrylevelanalysis$Country == 14] <- "India"
countrylevelanalysis$Country[countrylevelanalysis$Country == 15] <- "Indonesia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 16] <- "Italy"
countrylevelanalysis$Country[countrylevelanalysis$Country == 17] <- "Japan"
countrylevelanalysis$Country[countrylevelanalysis$Country == 18] <- "Kenya"
countrylevelanalysis$Country[countrylevelanalysis$Country == 19] <- "Malaysia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 20] <- "Mexico"
countrylevelanalysis$Country[countrylevelanalysis$Country == 21] <- "Morocco"
countrylevelanalysis$Country[countrylevelanalysis$Country == 22] <- "Netherlands"
countrylevelanalysis$Country[countrylevelanalysis$Country == 23] <- "New Zealand"
countrylevelanalysis$Country[countrylevelanalysis$Country == 24] <- "Nigeria"
countrylevelanalysis$Country[countrylevelanalysis$Country == 25] <- "Pakistan"
countrylevelanalysis$Country[countrylevelanalysis$Country == 26] <- "Panama"
countrylevelanalysis$Country[countrylevelanalysis$Country == 27] <- "Peru"
countrylevelanalysis$Country[countrylevelanalysis$Country == 28] <- "Philippines"
countrylevelanalysis$Country[countrylevelanalysis$Country == 29] <- "Poland"
countrylevelanalysis$Country[countrylevelanalysis$Country == 30] <- "Portugal"
countrylevelanalysis$Country[countrylevelanalysis$Country == 31] <- "Russia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 32] <- "Serbia"
countrylevelanalysis$Country[countrylevelanalysis$Country == 33] <- "Singapore"
countrylevelanalysis$Country[countrylevelanalysis$Country == 34] <- "South Africa"
countrylevelanalysis$Country[countrylevelanalysis$Country == 35] <- "South Korea"
countrylevelanalysis$Country[countrylevelanalysis$Country == 36] <- "Spain"
countrylevelanalysis$Country[countrylevelanalysis$Country == 37] <- "Sweden"
countrylevelanalysis$Country[countrylevelanalysis$Country == 38] <- "Taiwan"
countrylevelanalysis$Country[countrylevelanalysis$Country == 39] <- "Turkey"
countrylevelanalysis$Country[countrylevelanalysis$Country == 40] <- "UK"
countrylevelanalysis$Country[countrylevelanalysis$Country == 41] <- "US"
countrylevelanalysis$Country[countrylevelanalysis$Country == 42] <- "Venezuela"

countrylevelanalysis$Country <- as.factor(countrylevelanalysis$Country)
```

## Assigning Venezuela GDP_PPP according to https://data.worldbank.org/indicator/NY.GDP.PCAP.PP.CD?locations=VE
```{r}
countrylevelanalysis$GDP_PPP[countrylevelanalysis$Country %in% "Venezuela"] <- "4500"
```

## Groupwise correlation
```{r}
smallcla <- subset(countrylevelanalysis, select = c(
  "System_Justification", "GDP_PPP", "GINI_UN",
  "Democracy_Index", "Factionalized_Elites",
  "State_Legitimacy_Index", "Ind_Col","Life_Satisfaction"
))

smallcla$System_Justification <- as.numeric(smallcla$System_Justification)
smallcla$GDP_PPP <- as.numeric(smallcla$GDP_PPP)
smallcla$GINI_UN <- as.numeric(smallcla$GINI_UN)
smallcla$Democracy_Index <- as.numeric(smallcla$Democracy_Index)
smallcla$Factionalized_Elites <- as.numeric(smallcla$Factionalized_Elites)
smallcla$State_Legitimacy_Index <- as.numeric(smallcla$State_Legitimacy_Index)
smallcla$Ind_Col <- as.numeric(smallcla$Ind_Col)
smallcla$Life_Satisfaction <- as.numeric(smallcla$Life_Satisfaction)

chart.Correlation(smallcla)

apa.cor.table(smallcla, filename = "Countrylevelmoderators_DI2.doc")
```


## Full data - indvidual level analysis
```{r}
## Getting NA's instead of blanks for income and Salary

dat2 <- full_evan_dataset %>% mutate_at(
  .vars = c(
    "Income_1", "Income_2",
    "Income_3", "Income_4", "Salary_1", "Salary_2",
    "Salary_3", "Salary_4", "System_Justification"
  ),
  .funs = list(~ ifelse(. == "", NA, as.character(.)))
)
```

## Attaching country names
```{r}
dat2$Country <- as.character(dat2$Country)
dat2$Country[dat2$Country == 1] <- "Argentina"
dat2$Country[dat2$Country == 2] <- "Australia"
dat2$Country[dat2$Country == 3] <- "Bolivia"
dat2$Country[dat2$Country == 4] <- "Brazil"
dat2$Country[dat2$Country == 5] <- "Canada"
dat2$Country[dat2$Country == 6] <- "China"
dat2$Country[dat2$Country == 7] <- "Colombia"
dat2$Country[dat2$Country == 8] <- "Egypt"
dat2$Country[dat2$Country == 9] <- "Finland"
dat2$Country[dat2$Country == 10] <- "Germany"
dat2$Country[dat2$Country == 11] <- "Greece"
dat2$Country[dat2$Country == 12] <- "Hong Kong"
dat2$Country[dat2$Country == 13] <- "Hungary"
dat2$Country[dat2$Country == 14] <- "India"
dat2$Country[dat2$Country == 15] <- "Indonesia"
dat2$Country[dat2$Country == 16] <- "Italy"
dat2$Country[dat2$Country == 17] <- "Japan"
dat2$Country[dat2$Country == 18] <- "Kenya"
dat2$Country[dat2$Country == 19] <- "Malaysia"
dat2$Country[dat2$Country == 20] <- "Mexico"
dat2$Country[dat2$Country == 21] <- "Morocco"
dat2$Country[dat2$Country == 22] <- "Netherlands"
dat2$Country[dat2$Country == 23] <- "New Zealand"
dat2$Country[dat2$Country == 24] <- "Nigeria"
dat2$Country[dat2$Country == 25] <- "Pakistan"
dat2$Country[dat2$Country == 26] <- "Panama"
dat2$Country[dat2$Country == 27] <- "Peru"
dat2$Country[dat2$Country == 28] <- "Philippines"
dat2$Country[dat2$Country == 29] <- "Poland"
dat2$Country[dat2$Country == 30] <- "Portugal"
dat2$Country[dat2$Country == 31] <- "Russia"
dat2$Country[dat2$Country == 32] <- "Serbia"
dat2$Country[dat2$Country == 33] <- "Singapore"
dat2$Country[dat2$Country == 34] <- "South Africa"
dat2$Country[dat2$Country == 35] <- "South Korea"
dat2$Country[dat2$Country == 36] <- "Spain"
dat2$Country[dat2$Country == 37] <- "Sweden"
dat2$Country[dat2$Country == 38] <- "Taiwan"
dat2$Country[dat2$Country == 39] <- "Turkey"
dat2$Country[dat2$Country == 40] <- "UK"
dat2$Country[dat2$Country == 41] <- "US"
dat2$Country[dat2$Country == 42] <- "Venezuela"

dat2$Country <- as.factor(dat2$Country)
```
## Creating new variable - grouping by region
```{r}
dat2$Region = NA
dat2$Region <- as.character(dat2$Region)
## Nordic
dat2$Region[dat2$Country %in% "Sweden"] <- "Nordic"
dat2$Region[dat2$Country %in% "Finland"] <- "Nordic"
## Anglo
dat2$Region[dat2$Country %in% "Australia"] <- "Anglo"
dat2$Region[dat2$Country %in% "New Zealand"] <- "Anglo"
dat2$Region[dat2$Country %in% "UK"] <- "Anglo"
dat2$Region[dat2$Country %in% "Canada"] <- "Anglo"
dat2$Region[dat2$Country %in% "US"] <- "Anglo"
## Western Europe
dat2$Region[dat2$Country %in% "Greece"] <- "Western Europe"
dat2$Region[dat2$Country %in% "Italy"] <- "Western Europe"
dat2$Region[dat2$Country %in% "Portugal"] <- "Western Europe"
dat2$Region[dat2$Country %in% "Spain"] <- "Western Europe"
dat2$Region[dat2$Country %in% "Germany"] <- "Western Europe"
dat2$Region[dat2$Country %in% "Netherlands"] <- "Western Europe"
## Confucian Asia
dat2$Region[dat2$Country %in% "Japan"] <- "Confucian Asia"
dat2$Region[dat2$Country %in% "South Korea"] <- "Confucian Asia"
dat2$Region[dat2$Country %in% "Taiwan"] <- "Confucian Asia"
dat2$Region[dat2$Country %in% "China"] <- "Confucian Asia"
dat2$Region[dat2$Country %in% "Hong Kong"] <- "Confucian Asia"
## Eastern Europe
dat2$Region[dat2$Country %in% "Hungary"] <- "Eastern Europe"
dat2$Region[dat2$Country %in% "Turkey"] <- "Eastern Europe"
dat2$Region[dat2$Country %in% "Serbia"] <- "Eastern Europe"
dat2$Region[dat2$Country %in% "Russia"] <- "Eastern Europe"
dat2$Region[dat2$Country %in% "Poland"] <- "Eastern Europe"
## South East Asia
dat2$Region[dat2$Country %in% "Singapore"] <- "South East Asia"
dat2$Region[dat2$Country%in% "Indonesia"] <- "South East Asia"
dat2$Region[dat2$Country %in% "Malaysia"] <- "South East Asia"
dat2$Region[dat2$Country %in% "Philippines"] <- "South East Asia"
## Latin America
dat2$Region[dat2$Country %in% "Bolivia"] <- "Latin America"
dat2$Region[dat2$Country %in% "Argentina"] <- "Latin America"
dat2$Region[dat2$Country %in% "Panama"] <- "Latin America"
dat2$Region[dat2$Country %in% "Peru"] <- "Latin America"
dat2$Region[dat2$Country %in% "Colombia"] <- "Latin America"
dat2$Region[dat2$Country %in% "Mexico"] <- "Latin America"
dat2$Region[dat2$Country %in% "Venezuela"] <- "Latin America"
dat2$Region[dat2$Country %in% "Brazil"] <- "Latin America"
## Northern Africa
dat2$Region[dat2$Country %in% "Egypt"] <- "Northern Africa"
dat2$Region[dat2$Country %in% "Morocco"] <- "Northern Africa"
## SubS. Africa
dat2$Region[dat2$Country %in% "South Africa"] <- "SubS. Africa"
dat2$Region[dat2$Country %in% "Kenya"] <- "SubS. Africa"
dat2$Region[dat2$Country %in% "Nigeria"] <- "SubS. Africa"
## South Asian
dat2$Region[dat2$Country %in% "Pakistan"] <- "South Asian"
dat2$Region[dat2$Country %in% "India"] <- "South Asian"

```

## exploring missing data
```{r}
any(is.na(dat2))

sum(is.na(dat2))

colSums(is.na(dat2))

which(is.na(dat2$Country))


## Removing missing values from the country column
dat2 <- dat2[!(is.na(dat2$Country)), ]
dat2 <- dat2[!(is.na(dat2$PolOrientation)), ]
dat2 <- dat2[!(is.na(dat2$Conspiracy_Theory)), ]
```

## Summary of income data
```{r}
options(scipen = 999) # turning off scientific notation
summary(dat2$Income_1)
summary(dat2$Income_2)
summary(dat2$Income_3)
summary(dat2$Income_4)
```

## Creating new variable - how did participants report income
```{r}
dat2$income_report = NA
dat2$income_report <- as.character(dat2$income_report)

dat2[ which(dat2$Income_1 != FALSE), "income_report" ] = "Daily" 
dat2[ which(dat2$Income_2 != FALSE), "income_report" ] = "Weekly"
dat2[ which(dat2$Income_3 != FALSE), "income_report" ] = "Monthly"
dat2[ which(dat2$Income_4 != FALSE), "income_report" ] = "Annually"

dat2$income_report <- factor(dat2$income_report, levels = c("Annually", "Monthly",
                                                            "Weekly", "Daily"))
```


## Bar plot of income reporting styles by country
```{r}
library(forcats)
 
   ggplot(dat2, aes(x = Country, fill = income_report)) +
  geom_bar(width = 0.6, size = 0.6, alpha = 0.8, position = position_fill(reverse = TRUE)) +
  scale_fill_discrete(
    name = "Income Report",
    labels = c("Annually", "Monthly", "Weekly", "Daily", "NA Missing Data")
  ) +
  theme(
    text = element_text(size = 10),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = .2)
  ) +
  labs(title = "Income Report Stacked Barplot")
```

## Changing income_report variable from character to numeric
## daily = 1 / weekly = 2 / monthly = 3 / annually = 4

```{r}
dat2$income_report2 = NA

dat2$income_report2[dat2$income_report == "Daily"] = "1"
dat2$income_report2[dat2$income_report == "Weekly"] = "2"
dat2$income_report2[dat2$income_report == "Monthly"] = "3"
dat2$income_report2[dat2$income_report == "Annually"] = "4"

dat2$income_report2 <- as.numeric(dat2$income_report2)
```

## Conspiracy theory graphs of interest
```{r}
dat2$Conspiracy_Theory <- as.numeric(dat2$Conspiracy_Theory)
dat2$PolOrientation <- as.factor(dat2$PolOrientation)

dat2 %>% ggplot(aes(x = PolOrientation, y = Conspiracy_Theory)) +
        geom_col(aes(fill = PolOrientation))

dat2 %>% ggplot(aes(x = PolEngagement_Voting, y =Conspiracy_Theory)) +
        geom_col(aes(fill = PolEngagement_Voting))

dat2 %>% ggplot(aes(x = PolEngagement_Civic, y =Conspiracy_Theory)) +
        geom_col(aes(fill = PolEngagement_Voting))

dat2 %>% ggplot(aes(x = System_Justification, y =Conspiracy_Theory)) +
        geom_col(aes(fill = PolEngagement_Voting))
## build a profile based upon these measures for who is conspiracy thinking
## think cross-culturally - country level indexes in relation to conspiracy 
## thinking 
## cor con and pol interest
cor(dat2$Conspiracy_Theory, dat2$PolEngagement_Voting, use = "complete.obs")
cor(dat2$Conspiracy_Theory, dat2$PolEngagement_Civic, use = "complete.obs")
cor(dat2$Conspiracy_Theory, dat2$PolEngagement_Voice, use = "complete.obs")

cor(dat2$Conspiracy_Theory, dat2$System_Justification, use = "complete.obs")

dat2$System_Justification <- as.numeric(dat2$System_Justification)
## look for media measures


```

## Creating Social Mobility index
## Data accessed from https://www.weforum.org/reports/global-social-mobility-index-2020-why-economies-benefit-from-fixing-inequality/#country-rankings 
```{r}
dat3 <- dat2 %>%
  mutate(Social_Mobility = ifelse(Country == "Argentina", 57.3,
    ifelse(Country == "Australia", 75.1,
      ifelse(Country == "Brazil", 52.1,
        ifelse(Country == "Bolivia", 48.2,
          ifelse(Country == "Canada", 76.1,
            ifelse(Country == "China", 61.5,
              ifelse(Country == "Columbia", 59.3,
                ifelse(Country == "Egypt", 44.8,
                  ifelse(Country == "Finland", 83.6,
                    ifelse(Country == "Germany", 78.8,
                      ifelse(Country == "Greece", 59.8,
                        ifelse(Country == "Hong Kong", 61.5,
                          ifelse(Country == "Hungary", 65.8,
                            ifelse(Country == "India", 42.7,
                              ifelse(Country == "Indonesia", 49.3,
                                ifelse(Country == "Italy", 67.4,
                                  ifelse(Country == "Japan", 76.1,
                                    ifelse(Country == "Kenya", NA,
                                      ifelse(Country == "Malaysia", 62.0,
                                        ifelse(Country == "Mexico", 52.6,
                                          ifelse(Country == "Morocco", NA,
                                            ifelse(Country == "Netherlands", 82.4,
                                              ifelse(Country == "New Zealand", 74.3,
                                                ifelse(Country == "Nigeria", NA,
                                                  ifelse(Country == "Pakistan", 36.7,
                                                    ifelse(Country == "Panama", 51.4,
                                                      ifelse(Country == "Peru", 49.9,
                                                        ifelse(Country == "Philippines", 51.7,
                                                          ifelse(Country == "Poland", 69.1,
                                                            ifelse(Country == "Portugal", 72.0,
                                                              ifelse(Country == "Russia", 64.7,
                                                                ifelse(Country == "Serbia", 63.8,
                                                                  ifelse(Country == "Singapore", 74.6,
                                                                    ifelse(Country == "South Africa", 41.4,
                                                                      ifelse(Country == "South Korea", 71.4,
                                                                        ifelse(Country == "Spain", 70.0,
                                                                          ifelse(Country == "Sweden", 83.5,
                                                                            ifelse(Country == "Taiwan", 61.5,
                                                                              ifelse(Country == "Turkey", 51.3,
                                                                                ifelse(Country == "UK", 74.4,
                                                                                  ifelse(Country == "US", 70.4,
                                                                                    ifelse(Country == "Venezuela", 64.4,
                                                                                           "")
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))

```

## Adding GINI coeffcient scores (larger scores indicate greater inequality)
## Adding Freedom/Civil Liberty Scores (Larger scores indicate greater freedom)
```{r}
dat4 <- dat3 %>%
  mutate(GINI = ifelse(Country == "Argentina", 42.3,
    ifelse(Country == "Australia", 33.0,
      ifelse(Country == "Brazil", 48.9,
        ifelse(Country == "Bolivia", 43.6,
          ifelse(Country == "Canada", 33.0,
            ifelse(Country == "China", 48.0,
              ifelse(Country == "Columbia", 54.2,
                ifelse(Country == "Egypt", 31.0,
                  ifelse(Country == "Finland", 27.0,
                    ifelse(Country == "Germany", 31.0,
                      ifelse(Country == "Greece", 33.0,
                        ifelse(Country == "Hong Kong", 53.0,
                          ifelse(Country == "Hungary", 30.0,
                            ifelse(Country == "India", 47.0,
                              ifelse(Country == "Indonesia", 37.0,
                                ifelse(Country == "Italy", 35.0,
                                  ifelse(Country == "Japan", 29.0,
                                    ifelse(Country == "Kenya", 41.0,
                                      ifelse(Country == "Malaysia", 42.0,
                                        ifelse(Country == "Mexico", 45.4,
                                          ifelse(Country == "Morocco", 35.0,
                                            ifelse(Country == "Netherlands", 29.0,
                                              ifelse(Country == "New Zealand", 32.0,
                                                ifelse(Country == "Nigeria", 35.0,
                                                  ifelse(Country == "Pakistan", 29.0,
                                                    ifelse(Country == "Panama", 49.0,
                                                      ifelse(Country == "Peru", 43.8,
                                                        ifelse(Country == "Philippines", 42.0,
                                                          ifelse(Country == "Poland", 30.0,
                                                            ifelse(Country == "Portugal", 32.0,
                                                              ifelse(Country == "Russia", 35.0,
                                                                ifelse(Country == "Serbia", 34.0,
                                                                  ifelse(Country == "Singapore", 35.6,
                                                                    ifelse(Country == "South Africa", 63.0,
                                                                      ifelse(Country == "South Korea", 31.0,
                                                                        ifelse(Country == "Spain", 34.0,
                                                                          ifelse(Country == "Sweden", 26.0,
                                                                            ifelse(Country == "Taiwan", 34.0,
                                                                              ifelse(Country == "Turkey", 41.0,
                                                                                ifelse(Country == "UK", 36.0,
                                                                                  ifelse(Country == "US", 41.0,
                                                                                    ifelse(Country == "Venezuela", 46.0,
                                                                                           "")
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))

dat5 <- dat4 %>%
  mutate(Freedom = ifelse(Country == "Argentina", 84,
    ifelse(Country == "Australia", 95,
      ifelse(Country == "Brazil", 73,
        ifelse(Country == "Bolivia", 66,
          ifelse(Country == "Canada", 98,
            ifelse(Country == "China", 9,
              ifelse(Country == "Columbia", 64,
                ifelse(Country == "Egypt", 18,
                  ifelse(Country == "Finland", 100,
                    ifelse(Country == "Germany", 94,
                      ifelse(Country == "Greece", 87,
                        ifelse(Country == "Hong Kong", 43,
                          ifelse(Country == "Hungary", 69,
                            ifelse(Country == "India", 66,
                              ifelse(Country == "Indonesia", 59,
                                ifelse(Country == "Italy", 90,
                                  ifelse(Country == "Japan", 96,
                                    ifelse(Country == "Kenya", 48,
                                      ifelse(Country == "Malaysia", 66,
                                        ifelse(Country == "Mexico", 60,
                                          ifelse(Country == "Morocco", 37,
                                            ifelse(Country == "Netherlands", 97,
                                              ifelse(Country == "New Zealand", 99,
                                                ifelse(Country == "Nigeria", 43,
                                                  ifelse(Country == "Pakistan", 37,
                                                    ifelse(Country == "Panama", 83,
                                                      ifelse(Country == "Peru", 72,
                                                        ifelse(Country == "Philippines", 55,
                                                          ifelse(Country == "Poland", 81,
                                                            ifelse(Country == "Portugal", 95,
                                                              ifelse(Country == "Russia", 19,
                                                                ifelse(Country == "Serbia", 62,
                                                                  ifelse(Country == "Singapore", 47,
                                                                    ifelse(Country == "South Africa", 79,
                                                                      ifelse(Country == "South Korea", 83,
                                                                        ifelse(Country == "Spain", 90,
                                                                          ifelse(Country == "Sweden", 100,
                                                                            ifelse(Country == "Taiwan", 94,
                                                                              ifelse(Country == "Turkey", 32,
                                                                                ifelse(Country == "UK", 93,
                                                                                  ifelse(Country == "US", 83,
                                                                                    ifelse(Country == "Venezuela", 14,
                                                                                           "")
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))

```


## Adding political party in power
## Data collected from https://datacatalog.worldbank.org/search/dataset/0039819
## 0 = right, 1 = center, 2 = left
```{r}
dat6 <- dat5 %>%
  mutate(polpartypower = ifelse(Country == "Argentina", 2,
    ifelse(Country == "Australia", 2,
      ifelse(Country == "Brazil", 2,
        ifelse(Country == "Bolivia", 2,
          ifelse(Country == "Canada", 0,
            ifelse(Country == "China", 2,
              ifelse(Country == "Columbia", 0,
                ifelse(Country == "Egypt", 1,
                  ifelse(Country == "Finland", 0,
                    ifelse(Country == "Germany", 0,
                      ifelse(Country == "Greece", 2,
                        ifelse(Country == "Hong Kong", 1,
                          ifelse(Country == "Hungary", 0,
                            ifelse(Country == "India", 2,
                              ifelse(Country == "Indonesia", 2,
                                ifelse(Country == "Italy", 0,
                                  ifelse(Country == "Japan", 0,
                                    ifelse(Country == "Kenya", 1,
                                      ifelse(Country == "Malaysia", 2,
                                        ifelse(Country == "Mexico", 0,
                                          ifelse(Country == "Morocco", 0,
                                            ifelse(Country == "Netherlands", 2,
                                              ifelse(Country == "New Zealand", 2,
                                                ifelse(Country == "Nigeria", 0,
                                                  ifelse(Country == "Pakistan", 2,
                                                    ifelse(Country == "Panama", 1,
                                                      ifelse(Country == "Peru", 2,
                                                        ifelse(Country == "Philippines", 1,
                                                          ifelse(Country == "Poland", 1,
                                                            ifelse(Country == "Portugal", 0,
                                                              ifelse(Country == "Russia", 1,
                                                                ifelse(Country == "Serbia", 2,
                                                                  ifelse(Country == "Singapore", 1,
                                                                    ifelse(Country == "South Africa", 2,
                                                                      ifelse(Country == "South Korea", 2,
                                                                        ifelse(Country == "Spain", 2,
                                                                          ifelse(Country == "Sweden", 2,
                                                                            ifelse(Country == "Taiwan", 0,
                                                                              ifelse(Country == "Turkey", 0,
                                                                                ifelse(Country == "UK", 0,
                                                                                  ifelse(Country == "US", 0,
                                                                                    ifelse(Country == "Venezuela", 2,
                                                                                           "")
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))
```

## Making a subset of the data for income cleaning purposes
```{r}
INCOMECLEAN <- subset(dat6, select = c(
  "Country", "Region" ,"age", "Gender", "PolOrientation", "Total_Income_usd", 
  "PPP", "RegIncome", "income_report", "income_report2", "Education", "WellinSociety", 
  "Life_Satisfaction", "System_Justification", "Social_Mobility", "GINI", "Freedom",
  "polpartypower"
))

INCOMECLEAN$GINI <- as.numeric(INCOMECLEAN$GINI)
INCOMECLEAN$Freedom <- as.numeric(INCOMECLEAN$Freedom)
INCOMECLEAN$System_Justification <- as.numeric(INCOMECLEAN$System_Justification)
INCOMECLEAN$PolOrientation <- as.numeric(INCOMECLEAN$PolOrientation)
INCOMECLEAN$Total_Income_usd <- as.numeric(INCOMECLEAN$Total_Income_usd)
INCOMECLEAN$Education <- as.numeric(INCOMECLEAN$Education)
INCOMECLEAN$WellinSociety <- as.numeric(INCOMECLEAN$WellinSociety)
INCOMECLEAN$Life_Satisfaction <- as.numeric(INCOMECLEAN$Life_Satisfaction)
INCOMECLEAN$Social_Mobility <- as.numeric(INCOMECLEAN$Social_Mobility)
INCOMECLEAN$polpartypower <- as.numeric(INCOMECLEAN$polpartypower)
```

```{r}
smallcor <- subset(INCOMECLEAN, select = c("System_Justification", "Total_Income_usd",
                                           "Education", "WellinSociety", "PolOrientation" ,"Life_Satisfaction",
                                           "Social_Mobility", "GINI", "Freedom", "polpartypower"))

chart.Correlation(smallcor)

```

## Creating new annual income variable based upon income 1 - 4
## PIPE OPERATOR = SHIFT + CTRL + M (AND THEN)
```{r}
INCOMECLEAN$Total_Income = NA
INCOMECLEAN$Total_Income <- as.numeric(INCOMECLEAN$Total_Income)

INCOMECLEAN <- INCOMECLEAN %>% mutate(
  Total_Income =
    dplyr::coalesce(
      Income_4, 12 * Income_3, 52 * Income_2,
      365 * Income_1
    )
)

```

```{r}

annual_inc  <- function(Income_1, Income_2, Income_3, Income_4){
  if (is.na(Income_1) == FALSE) Income_1*365
  else if (is.na(Income_2) == FALSE) Income_2*52
  else if (is.na(Income_3) == FALSE) Income_3*12
  else if (is.na(Income_4) == FALSE) Income_4
  else NA}

INCOMECLEAN$annual_inc = mapply(FUN = annual_inc, INCOMECLEAN$Income_1, INCOMECLEAN$Income_2, INCOMECLEAN$Income_3, INCOMECLEAN$Income_4)
```

## Creating Purchasing Power Parity column 
```{r}
INCOMECLEAN$PPP = NA
INCOMECLEAN$PPP <- as.numeric(INCOMECLEAN$PPP)

```

## Converting income to USD to calculate PPP
## Conversion rates and purchasing power parity conversion factors were accessed and recorded on 10/25/21
## From https://www.xe.com/currencyconverter/ and ##https://data.oecd.org/conversion/purchasing-power-parities-ppp.htm
```{r}

INCOMECLEAN2 <- INCOMECLEAN %>%
  mutate(Total_Income_usd = ifelse(Country == "Argentina", Total_Income / 99,
    ifelse(Country == "Australia", Total_Income / 1.33,
      ifelse(Country == "Brazil", Total_Income / 5.63,
        ifelse(Country == "Bolivia", Total_Income / 6.89,
          ifelse(Country == "Canada", Total_Income / 1.23,
            ifelse(Country == "China", Total_Income / 6.39,
              ifelse(Country == "Columbia", Total_Income / 3782.26,
                ifelse(Country == "Egypt", Total_Income / 15.70,
                  ifelse(Country == "Finland", Total_Income / .85,
                    ifelse(Country == "Germany", Total_Income / .85,
                      ifelse(Country == "Greece", Total_Income / .85,
                        ifelse(Country == "Hong Kong", Total_Income / 7.77,
                          ifelse(Country == "Hungary", Total_Income / 311.77,
                            ifelse(Country == "India", Total_Income / 74.84,
                              ifelse(Country == "Indonesia", Total_Income / 14127.27,
                                ifelse(Country == "Italy", Total_Income / .85,
                                  ifelse(Country == "Japan", Total_Income / 113,
                                    ifelse(Country == "Kenya", Total_Income / 111,
                                      ifelse(Country == "Malaysia", Total_Income / 4.15,
                                        ifelse(Country == "Mexico", Total_Income / 20.24,
                                          ifelse(Country == "Morocco", Total_Income / 9.03,
                                            ifelse(Country == "Netherlands", Total_Income / .85,
                                              ifelse(Country == "New Zealand", Total_Income / 1.39,
                                                ifelse(Country == "Nigeria", Total_Income / 410.75,
                                                  ifelse(Country == "Pakistan", Total_Income / 173.58,
                                                    ifelse(Country == "Panama", Total_Income / 1,
                                                      ifelse(Country == "Peru", Total_Income / 3.95,
                                                        ifelse(Country == "Philippines", Total_Income / 50.80,
                                                          ifelse(Country == "Poland", Total_Income / 3.94,
                                                            ifelse(Country == "Portugal", Total_Income / .85,
                                                              ifelse(Country == "Russia", Total_Income / 71.15,
                                                                ifelse(Country == "Serbia", Total_Income / 100,
                                                                  ifelse(Country == "Singapore", Total_Income / 1.34,
                                                                    ifelse(Country == "South Africa", Total_Income / 14.55,
                                                                      ifelse(Country == "South Korea", Total_Income / 1177,
                                                                        ifelse(Country == "Spain", Total_Income / .85,
                                                                          ifelse(Country == "Sweden", Total_Income / 8.59,
                                                                            ifelse(Country == "Taiwan", Total_Income / 27.87,
                                                                              ifelse(Country == "Turkey", Total_Income / 9.43,
                                                                                ifelse(Country == "UK", Total_Income / .72,
                                                                                  ifelse(Country == "US", Total_Income / 1,
                                                                                    ifelse(Country == "Venezuela", Total_Income / 418223.84,
                                                                                      ""
                                                                                    )
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))
```

## ## Correlations between total income variables and perception of 
## income stability and SJ after converting income to USD %
```{r}
INCOMECLEAN2$income_percent = NA
INCOMECLEAN2$income_percent <- rank(INCOMECLEAN2$Total_Income_usd)/length(INCOMECLEAN2$Total_Income_usd)*100

INCOMECLEAN2$Gender <- as.numeric(INCOMECLEAN2$Gender)
INCOMECLEAN2$age <- as.numeric(INCOMECLEAN2$age)
INCOMECLEAN2$PolOrientation <- as.numeric(INCOMECLEAN2$PolOrientation)
INCOMECLEAN2$Education <- as.numeric(INCOMECLEAN2$Education)
INCOMECLEAN2$WellinSociety <- as.numeric(INCOMECLEAN2$WellinSociety)
INCOMECLEAN2$income_percent <- as.numeric(INCOMECLEAN2$income_percent)
INCOMECLEAN2$RegIncome <- as.numeric(INCOMECLEAN2$RegIncome)
INCOMECLEAN2$Rel_Mobility <- as.numeric(INCOMECLEAN2$Rel_Mobility)
INCOMECLEAN2$System_Justification <- as.numeric(INCOMECLEAN2$System_Justification)
INCOMECLEAN2$Identity2 <- as.numeric(INCOMECLEAN2$Identity2)
INCOMECLEAN2$GlobalTrustInventory_GVT <- as.numeric(INCOMECLEAN2$GlobalTrustInventory_GVT)
INCOMECLEAN2$income_report2 <- as.numeric(INCOMECLEAN2$income_report2)

incomecor <- subset(INCOMECLEAN2, select = c(
  income_percent, RegIncome, income_report2, Education, WellinSociety, PolOrientation,
  Life_Satisfaction, Conspiracy_Theory, GlobalTrustInventory_GVT,
  System_Justification, Gender, age, Identity2, Rel_Mobility  
))

chart.Correlation(incomecor)
```

## Country Wide Purchasing Power Parity (TI * PPP Factor)
```{r}
INCOMECLEAN2$Total_Income_usd <- as.numeric(INCOMECLEAN2$Total_Income_usd)
## multiply total income by PPP conversion factor
INCOMECLEAN2 <- INCOMECLEAN2 %>%
  mutate(PPP = ifelse(Country == "Argentina", Total_Income_usd * 28.674,
    ifelse(Country == "Australia", Total_Income_usd * 1.472,
      ifelse(Country == "Brazil", Total_Income_usd * 2.362,
        ifelse(Country == "Bolivia", Total_Income_usd * 2.6,
          ifelse(Country == "Canada", Total_Income_usd * 1.206,
            ifelse(Country == "China", Total_Income_usd * 4.106,
              ifelse(Country == "Columbia", Total_Income_usd * 1352.7,
                ifelse(Country == "Egypt", Total_Income_usd * 4.5,
                  ifelse(Country == "Finland", Total_Income_usd * .840,
                    ifelse(Country == "Germany", Total_Income_usd * .746,
                      ifelse(Country == "Greece", Total_Income_usd * .544,
                        ifelse(Country == "Hong Kong", Total_Income_usd * 6.083,
                          ifelse(Country == "Hungary", Total_Income_usd * 148.013,
                            ifelse(Country == "India", Total_Income_usd * 21.990,
                              ifelse(Country == "Indonesia", Total_Income_usd * 4673.649,
                                ifelse(Country == "Italy", Total_Income_usd * .663,
                                  ifelse(Country == "Japan", Total_Income_usd * 102.835,
                                    ifelse(Country == "Kenya", Total_Income_usd * 44,
                                      ifelse(Country == "Malaysia", Total_Income_usd * 1.6,
                                        ifelse(Country == "Mexico", Total_Income_usd * 9.522,
                                          ifelse(Country == "Morocco", Total_Income_usd * 3.970,
                                            ifelse(Country == "Netherlands", Total_Income_usd * .773,
                                              ifelse(Country == "New Zealand", Total_Income_usd * 1.445,
                                                ifelse(Country == "Nigeria", Total_Income_usd * 144.3,
                                                  ifelse(Country == "Pakistan", Total_Income_usd * 38.7,
                                                    ifelse(Country == "Panama", Total_Income_usd * .458,
                                                      ifelse(Country == "Peru", Total_Income_usd * 1.742,
                                                        ifelse(Country == "Philippines", Total_Income_usd * 19.511,
                                                          ifelse(Country == "Poland", Total_Income_usd * 1.782,
                                                            ifelse(Country == "Portugal", Total_Income_usd * .570,
                                                              ifelse(Country == "Russia", Total_Income_usd * 25.881,
                                                                ifelse(Country == "Serbia", Total_Income_usd * 41.126,
                                                                  ifelse(Country == "Singapore", Total_Income_usd * .881,
                                                                    ifelse(Country == "South Africa", Total_Income_usd * 6.933,
                                                                      ifelse(Country == "South Korea", Total_Income_usd * 861.824,
                                                                        ifelse(Country == "Spain", Total_Income_usd * .618,
                                                                          ifelse(Country == "Sweden", Total_Income_usd * 8.765,
                                                                            ifelse(Country == "Taiwan", Total_Income_usd * 13.34,
                                                                              ifelse(Country == "Turkey", Total_Income_usd * 2.19,
                                                                                ifelse(Country == "UK", Total_Income_usd * .700,
                                                                                  ifelse(Country == "US", Total_Income_usd * 1,
                                                                                    ifelse(Country == "Venezuela", Total_Income_usd * 2.7,
                                                                                      ""
                                                                                    )
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))

```

## Divide new PPP factor calculation by real exchange rate to get true PPP
```{r}
INCOMECLEAN2$PPP <- as.numeric(INCOMECLEAN2$PPP)

INCOMECLEAN2 <- INCOMECLEAN2 %>%
  mutate(PPP = ifelse(Country == "Argentina", PPP / 99,
    ifelse(Country == "Australia", PPP / 1.33,
      ifelse(Country == "Brazil", PPP / 5.63,
        ifelse(Country == "Bolivia", PPP / 6.89,
          ifelse(Country == "Canada", PPP / 1.23,
            ifelse(Country == "China", PPP / 6.39,
              ifelse(Country == "Columbia", PPP / 3782.26,
                ifelse(Country == "Egypt", PPP / 15.70,
                  ifelse(Country == "Finland", PPP / .85,
                    ifelse(Country == "Germany", PPP / .85,
                      ifelse(Country == "Greece", PPP / .85,
                        ifelse(Country == "Hong Kong", PPP / 7.77,
                          ifelse(Country == "Hungary", PPP / 311.77,
                            ifelse(Country == "India", PPP / 74.84,
                              ifelse(Country == "Indonesia", PPP / 14127.27,
                                ifelse(Country == "Italy", PPP / .85,
                                  ifelse(Country == "Japan", PPP / 113,
                                    ifelse(Country == "Kenya", PPP / 111,
                                      ifelse(Country == "Malaysia", PPP / 4.15,
                                        ifelse(Country == "Mexico", PPP / 20.24,
                                          ifelse(Country == "Morocco", PPP / 9.03,
                                            ifelse(Country == "Netherlands", PPP / .85,
                                              ifelse(Country == "New Zealand", PPP / 1.39,
                                                ifelse(Country == "Nigeria", PPP / 410.75,
                                                  ifelse(Country == "Pakistan", PPP / 173.58,
                                                    ifelse(Country == "Panama", PPP / 1,
                                                      ifelse(Country == "Peru", PPP / 3.95,
                                                        ifelse(Country == "Philippines", PPP / 50.80,
                                                          ifelse(Country == "Poland", PPP / 3.94,
                                                            ifelse(Country == "Portugal", PPP / .85,
                                                              ifelse(Country == "Russia", PPP / 71.15,
                                                                ifelse(Country == "Serbia", PPP / 100,
                                                                  ifelse(Country == "Singapore", PPP / 1.34,
                                                                    ifelse(Country == "South Africa", PPP / 14.55,
                                                                      ifelse(Country == "South Korea", PPP / 1177,
                                                                        ifelse(Country == "Spain", PPP / .85,
                                                                          ifelse(Country == "Sweden", PPP / 8.59,
                                                                            ifelse(Country == "Taiwan", PPP / 27.87,
                                                                              ifelse(Country == "Turkey", PPP / 9.43,
                                                                                ifelse(Country == "UK", PPP / .72,
                                                                                  ifelse(Country == "US", PPP / 1,
                                                                                    ifelse(Country == "Venezuela", PPP / 418223.84,
                                                                                      ""
                                                                                    )
                                                                                  )
                                                                                )
                                                                              )
                                                                            )
                                                                          )
                                                                        )
                                                                      )
                                                                    )
                                                                  )
                                                                )
                                                              )
                                                            )
                                                          )
                                                        )
                                                      )
                                                    )
                                                  )
                                                )
                                              )
                                            )
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
  ))

```





```{r}
INCOMECLEAN2 <- INCOMECLEAN2 %>% 
  mutate(PPP = signif(PPP))
  

```




## NOT RELEVANT CODE (FOR NOW)

## income descriptive stats by country

```{r}
vars_for_table <- c("Income_1", "Income_2", "Income_3", "Income_4", "Country")
CreateTableOne(vars = vars_for_table, data = dat2)
```


